---
title: "RBioFormats demo"
format: html
editor: visual
---

## Library installation

This script currently runs on the development versions of `CytoImageList` and `cytomapper`. They can be installed via:

```{r}
remotes::install_github("BodenmillerGroup/CytoImageList")
remotes::install_github("BodenmillerGroup/cytomapper", ref = "no_CIL")
```

## Download data

Here, I download a number of OME-TIFF files hosted on Zenodo.

```{r}
library(tools)
download.file("https://zenodo.org/record/7412972/files/ome.zip?download=1",
              destfile = "ome.zip", method = "wget")

unzip("ome.zip")

unlink("ome.zip")
```

## Loading the library and helper functions

```{r}
library(RBioFormats)
library(xml2)
library(CytoImageList)
source("helpers.R")
library(S4Vectors)
```

## Reading in data

The `read_ometiff` function is a custom function that reads in OME-TIFF files together with metadata into a `CytoImageList` object. It stores image information in an `AnnotatedImage` object.

```{r}
images <- read_ometiff("ome")

images

channelData(images)

images$Patient1_001.ome.tiff

mcols(images)
```

## Visualize images

As the `AnnotatedImage` class inherits from `Image`, the `CytoImageList` object can be directly visualized using `cytomapper`.

```{r, fig.width=12, fig.height=12}
library(cytomapper)

plotPixels(images, 
           colour_by = c("Yb173_Ecad", "Ho165_CD8a", "Ir191_DNA1"),
           bcg = list("Yb173_Ecad" = c(0, 10, 1),
                      "Ho165_CD8a" = c(0, 5, 1),
                      "Ir191_DNA1" = c(0, 5, 1)))
```
