---
title: "ZarrExperiment demo"
format: html
editor: visual
---

## Library installation

This script currently runs on the development versions of `CytoImageList` and `cytomapper`. They can be installed via:

```{r}
remotes::install_github("BodenmillerGroup/CytoImageList")
remotes::install_github("BodenmillerGroup/cytomapper", ref = "no_CIL")
```

## Download data

I host an example ZARR file on Dropbox as the cloud access for this file didn't work in the past.

```{r}
library(tools)
download.file("https://www.dropbox.com/s/klr08bgv22natwf/5514375.zarr.zip?dl=0",
              destfile = "zarr/5514375.zarr.zip", method = "wget")

unzip("zarr/5514375.zarr.zip", exdir = "zarr")

unlink("zarr/5514375.zarr.zip")
unlink("zarr/__MACOSX/")
```

## Load libraries

```{r libraries}
library(ZarrExperiment)
library(EBImage)
library(CytoImageList)
source("helpers.R")
```

## Read data

The `read_omengff` function is a custom function that reads in OME-NGFF files together with metadata into a `CytoImageList` object. It stores image information in an `Image` object in memory. The `res` parameters specifies the resolution of the read in images.

```{r}
images <- read_omengff("zarr", res = "0")
```

## Visualize image

The example image are 5D of the shape (x, y, c, z, t). The `cytomapper` package currently does not support 4D and 5D data and we need to subset intividual frames.

```{r}
library(cytomapper)

images_small <- endoapply(images, function(x){x[,,,10,1]})

plotPixels(images_small, 
           colour_by = c("NCAPD2", "NEG_Dextran", "DNA"),
           bcg = list("NCAPD2" = c(0, 5, 1),
                      "NEG_Dextran" = c(0, 5, 1),
                      "DNA" = c(0, 5, 1)))
```
